Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-16 manuscript.Rnw
Minor ms edits; small glitch in equation in Methods S1

\affil[1]{1 Hawkesbury Insitute for the Environment, University of Western Sydney, Hawkesbury Campus, First Floor, Building L9, Locked Bag 1797, Penrith, NSW 2751, Australia}
\affil[2]{Biological Sciences, Macquarie University, North Ryde, NSW 2109, Australia}
\affil[3]{See Supporting Information}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{\textbf{Overview of the global biomass and allometry database.} (a) Variables were measured on \Sexpr{nrow(dataset)} individual plants from \Sexpr{length(unique(dataset$species))} species. (b) Coverage of the dataset across global climate space. Grey hexagons indicate the number of 0.5\degree~cells with woody vegetation across the space. Colour symbols show the locations of sampled individuals for three dominat woody functional types.}
    \label{fig:figure1}
\end{figure}

@@

where $M_i$ is the biomass in some compartment (leaves, stems or roots), $a_i$ the annual allocation of NPP to that compartment, and $\tau_i$ the annual turnover of compartment $i$. It is thus easy to see that partitioning ($M_i/M_T$, where $M_T$ is total biomass) can be different from allocation ($a_i$) because turnover ($\tau_i$) differs strongly between compartments.

@@

$$
a = c_0H^c_1
$$

>>>>

\affil[1]{1 Hawkesbury Insitute for the Environment, University of Western Sydney, Locked Bag 1797, Penrith, NSW 2751, Australia}
\affil[2]{Biological Sciences, Macquarie University, North Ryde, NSW 2109, Australia}
\affil[3]{See Supporting Information}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{\textbf{Overview of the global biomass and allometry database.} (a) Variables were measured on \Sexpr{nrow(dataset)} individual plants from \Sexpr{length(unique(dataset$species))} species. (b) Coverage of the dataset across global climate space. Grey hexagons indicate the number of 0.5\degree~cells with woody vegetation across the space. Colour symbols show the locations of sampled individuals for three dominant woody functional types.}
    \label{fig:figure1}
\end{figure}

@@

where $M_i$ is the biomass in some compartment (leaves, stems or roots), $a_i$ the annual allocation of NPP to that compartment, and $\tau_i$ the annual turnover of compartment $i$. It is thus easy to see that partitioning ($M_i/M_T$, where $M_T$ is total biomass) can be different from allocation ($a_i$) because turnover ($\tau_i$) differs between leaf and wood biomass.

@@

$$
a = c_0H^{c_1}
$$
